A 38 Million Year Old Mini-Neptune in the Kepler Field

### 2021-09-17 paper/ms.tex
update ms & add GD driver

We considered three possible explanations for the anomaly: gravity
darkening, transit timing variations, and spot-crossing events.
Gravity darkening is based on the premise that the rapidly rotating
star becomes oblate, and brighter near the poles than the equator
\citep[{\it e.g.},][]{masuda_spin-orbit_2015}.  The fractional shape
change due to gravity darkening is on the order of $(P_{\rm
break}/P_{\rm rot})^2$, for $P_{\rm break}$ the break-up rotation
period, and $P_{\rm rot}$ the rotation period.  Using the parameters
from Table~\ref{tab:posterior}, this yields an expected 1.6\%
distortion of the $\approx$1.8\,ppt transit depth: {\it i.e.}, an
absolute deviation of $\approx$3\,ppm.  The observed residual has an
amplitude of $\approx 30\,{\rm ppm}$.  Since the expected signal is
smaller than the observed anomaly by an order of magnitude, gravity
darkening seems to be an unlikely explanation.

>>>>

We considered three possible explanations for the anomaly: gravity
darkening, transit timing variations, and spot-crossing events.
Gravity darkening is based on the premise that the rapidly rotating
star becomes oblate, and brighter near the poles than the equator
\citep[{\it e.g.},][]{masuda_spin-orbit_2015}.  The fractional shape
change due to gravity darkening is on the order of $(P_{\rm
break}/P_{\rm rot})^2$, for $P_{\rm break}$ the break-up rotation
period, and $P_{\rm rot}$ the rotation period.  Using the parameters
from Table~\ref{tab:posterior}, this yields an expected 1.4\%
distortion of the $\approx$1.8\,ppt transit depth: {\it i.e.}, an
absolute deviation of $\approx$2.5\,ppm.  The observed residual has a
semi-amplitude of $\approx 50\,{\rm ppm}$.  Since the expected signal is
smaller than the observed anomaly by over an order of magnitude, gravity
darkening seems to be an unlikely explanation.
